Constraining tensorial and scalar couplings with $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2014-12-05 tensor/draft/draft-tensor-op.tex
[tensor...draft.tex] 1) everything to be checked with EOS now in red color 2) preliminary final version of app B

%%
%% Comments
%%
\newcommand{\danny}[1]{{\color{purple}{#1}}}
\newcommand{\christoph}[1]{{\color{red}{#1}}}
\newcommand{\fred}[1]{{\color{green}{#1}}}
\newcommand{\todo}[1]{{\color{blue}{ {\bf ToDo: }{#1}}}}
\newcommand{\checked}[1]{{\color{magenta}{ {\bf Checked: }{#1}}}}

@@

\begin{figure*}
  \includegraphics[width=.24\textwidth]{plots/pdf/FH-1-6_vs_CT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/FH-15-22_vs_CT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-1-6_vs_CT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-15-22_vs_cT.pdf}
\\
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-1-6_vs_CT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-14-16_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-16-19_vs_CT.pdf}
  \caption{
    The sensitivity of $F_H^\mu$ [upper row: 1, 2], ${\cal B}(B^+ \to K^+ 
    \bar\mu\mu)$ [upper row: 3, 4] and ${\cal B}(B^0 \to K^{*0} \bar\mu\mu)$
    [lower row] integrated over $q^2$ at low and high $q^2$ to the tensorial
    coupling $\wilson{T}$. The bands represent the theory uncertainties at
    68\% probability. 
    For comparison two values of $\wilson[NP]{9} = 0$ (red) and $\wilson[NP]{9} 
    = -1.3$ (green) are shown together with the 68\% measurements of LHCb (blue).
  }
  \label{fig:FHvsCT}
\end{figure*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\ 
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  \hline \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.35,\, 0.20]$ ($[-0.55,\, 0.40]$) $\quad$
  & $\quad$ $[-0.20,\, 0.15]$ ($[-0.35,\, 0.30]$) $\quad$
  & $\quad$ $[-0.20,\, 0.20]$ ($[-0.40,\, 0.35]$) $\quad$
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)
  & $[-0.15,\, 0.15]$ ($[-0.30,\, 0.30]$)
  & $[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)
  & $[-0.10,\, 0.20]$ ($[-0.25,\, 0.35]$)
  & $[-0.20,\, 0.15]$ ($[-0.35,\, 0.35]$)
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)
  & $[-0.15,\, 0.15]$ ($[-0.30,\, 0.30]$)
  & $[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)
  \\
  \hline 
  $|\wilson{T}|$, $|\wilson{T5}|$
  & $< 0.35$ ($< 0.55$)
  & $< 0.25$ ($< 0.35$)
  & $< 0.30$ ($< 0.45$)
  \\
  \hline 
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ --- [upper] 1D-marginalized 
     at 68\% (95\%) probability and [lower] 2D-marginalized --- when using
     measurements of $i)$ only $F_H^\mu$, $ii)$ $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $B_s \to \bar\mu\mu$), and $iii)$ allowing
     also new physics contributions to $\wilson{9,\,10}$ with uniform prior
     $\wilson[NP]{i} \in [-3,\, 3]$.
  }
\end{table*}

In a scenario with only tensorial complex-valued couplings $\wilson{T,\, T5}$,
the experimental measurement of $F_H^\mu$ constrains the combination
$|\wilson{T}|^2 + |\wilson{T5}|^2$, up to some small interference of
$\wilson{T}$ with vectorial couplings $\wilson{7,\,7',\,9,\,9'}$. 
The according 65\% (95\%) 1D-marginalized probability intervals are listed in
\reftab{tab:cTT5:1-dimCLs}. As can be seen further in \reftab{tab:cTT5:1-dimCLs},
the constraints become tighter when utilising all observables in
\reftab{tab:observables}, mainly due to the branching ratio of $B\to K^{*} 
\bar\mu\mu$. The latter stronger bounds are driven by the new lattice
results of $B\to K^*$ form factors that yield too high predictions compared
to the measurements~\cite{Horgan:2013pva}. Since tensorial couplings contribute
constructively to ${\cal B}(B\to K^{*}\bar\mu\mu)$ large values are stronger
constrained. In this scenario, the measurements of $A_{\rm FB}^\mu$ does not pose
constraints due to vanishing scalar couplings and we find that the rate 
CP-asymmetries $A_{\rm CP}$ of $B\to K^{(*)} \bar\mu\mu$ do not provide 
constraints, therefore omitting them.

Eventually, we perform a fit with non-zero complex-valued $\wilson{9,\,10}$
by allowing uniform priors for $\mbox{Re, Im}(\wilson[NP]{i}) \in[-3,\, 3]$,
($i = 9,10$) in order to access the stability of the bounds derived from $F_H^\mu$
against destructive interference. In this case, $F_H^\mu$ by itself still provides 
bounds $|\wilson{T,\,T5}| < 0.5\,(0.8)$ at 68\% (95\%) probability that are
weakened by a factor of two since $F_H^\mu$ does not pose constraints on
$\wilson{9,\,10}$ (in the chosen prior range). Once additional experimental
measurements of \reftab{tab:observables}
are taken into account, the potential destructive effects of new physics
in $\wilson{9,\,10}$ become reduced and one recovers almost the same
constraints on $\wilson{T,\,T5}$ shown in \reftab{tab:cTT5:1-dimCLs}.
In consequence, the $F_H^\mu$ measurement~\cite{Aaij:2014tfa} of LHCb with
3 fb$^{-1}$ improves the previous bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$ 
by a factor of two.

@@

The according four-parameter fit for real-valued scalar couplings to the data of
$\overline{\cal B}(B_s \to \bar\mu\mu)$ and $F_H^\mu$ results in the (2D-marginalized)
regions in the $(\wilson{i} \pm \wilson{i'})$ ($i = S, P$)  planes shown in
\reffig{fig:scalar}. The combination of $\overline{\cal B}(B_s \to \bar\mu\mu)$ 
and $F_H^\mu$ does not change when including the data of ${\cal B}$'s of $B\to 
K^{(*)}\bar\mu\mu$ --- remember that $A_{\rm FB}^\mu$ requires interference of
scalar with tensorial couplings. Quantitatively, the constraint from $\overline{\cal B}
(B_s \to \bar\mu\mu)$ on $(\wilson{i} - \wilson{i'})$ is about a factor five
stronger than the one of $F_H^\mu$ on $(\wilson{i} + \wilson{i'})$.

\begin{figure*}
  \includegraphics[width=.325\textwidth]{plots/pdf/res-SSp.pdf}
%  \includegraphics[width=.32\textwidth]{plots/pdf/res-PPp.pdf}
  \includegraphics[width=.325\textwidth]{plots/pdf/res-SPplus.pdf}
  \includegraphics[width=.325\textwidth]{plots/pdf/res-SPminus.pdf}
  \caption{
    Constraints on real-valued scalar couplings $\wilson{S,\,S',\,P,\,P'}$ 
    from only $F_H^\mu$~(blue), only $\overline{\cal B}(B_s \to \bar\mu\mu)$ (green) 
    and their combination with other data in \reftab{tab:observables} as well as
    $\wilson{10} \in [-1,\, 9]$, $\wilson{10'} \in [-5,\,5]$ (red) 
    at 68\% (darker) and 95\% (lighter) probability. The constraints on 
    $(\wilson{P}Ê\pm \wilson{P'})$ are identical to $(\wilson{S}Ê\pm \wilson{S'})$
    [left], apart from a small shift of the contours by $(+0.2,\, 0.15)$.
  }
  \label{fig:scalar}
\end{figure*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & only $\overline{\cal B}(B_s \to \bar\mu\mu)$
  & all
  \\ 
  set of couplings
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P'\,10,\,10'}$
  \\
  \hline \hline
  $\mbox{Re}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & $\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$
  & $\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$
  \\
  $\mbox{Im}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & $\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$
  & $\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$
  \\[0.1cm]
  $\mbox{Re}(\wilson{S} + \wilson{S'})$
  & $[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)
  & $-$
  & $[-0.3,\, 0.4]$ ($[-0.6,\, 0.7]$)
  \\
  $\mbox{Im}(\wilson{S} + \wilson{S'})$
  & $[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)
  & $-$
  & $[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} - \wilson{P'})$
  & $-$
  & $[0.06,\, 0.20]$  ($[0.02,\, 0.25]$)
  & $[-0.10,\, 0.10]$ ($[-0.18,\, 0.18]$)
  \\
  $\mbox{Im}(\wilson{P} - \wilson{P'})$
  & $-$
  & $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$)
  & $[-0.10,\, 0.10]$ ($[-0.20,\, 0.20]$)
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} + \wilson{P'})$
  & $[-0.2,\, 0.6]$ ($[-0.5,\, 0.9]$)
  & $-$
  & $[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)
  \\
  $\mbox{Im}(\wilson{P} + \wilson{P'})$
  & $[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)
  & $-$
  & $[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)
  \\
  \hline 
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cSP:1-dimCLs}
     The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$ --- 1D-marginalized 
     at 65\% (95\%) probability --- when using measurements of $i)$ only $F_H^\mu$,
     $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $iii)$ all the data in
     \reftab{tab:observables} allowing also for new physics contributions to 
     $\wilson{10,\,10'}$ with uniform prior $\mbox{Re}\,\wilson[NP]{10} \in [-1,\, 9]$,
     $\mbox{Im}\,(\wilson[NP]{10})$ and $\mbox{Re},\mbox{Im}\,(\wilson[NP]{10'}) \in [-5,\, 5]$.
  }
\end{table*}

@@

We find that the experimental measurement of $F_H^\mu$
\begin{enumerate}
\item imposes by itself constraints on tensorial couplings $|{\cal C}_{T,\,T5}^\mu|
  < 0.35\, (0.55)$ at 68\% (95\%) probability, superseding previous bounds.
  In combination with current data from $B\to K^* \bar\mu\mu$ and lattice
  $B\to K^*$ form factors they become tighter $|{\cal C}_{T,\,T5}^\mu| < 0.30\, 
  (0.45)$, even in the presence of non-standard contributions in vectorial
  couplings.
\item allows for the first time to bound all four scalar and pseudo-scalar 
  couplings due to it's complementarity to $\overline{\cal B}(B_s \to \bar\mu\mu)$.
  Even when taking into account destructive interference with vectorial couplings
  $|\wilson{i} + \wilson{i'}| < 0.4\, (0.7)$ and $|\wilson{i} - \wilson{i'}| < 
  0.1\, (0.2)$ for $i = S,P$. Currently, the bounds from $F_H^\mu$ are not as
  strong as those from $\overline{\cal B}(B_s \to \bar\mu\mu)$ by a factor four.
  Future measurements at LHCb and Belle II might change this, especially for 
  $\ell = e$. 
\item SM-EFT $\ldots$
\end{enumerate}
In all cases these constraints are weakened only slightly in the presence of
new physics in vectorial couplings from destructive interference.

@@

@@

Concerning numerical input, we refer the reader to~\cite{Beaujean:2013soa} for
the compilation of nuisance parameters and according values, whose uncertainties
are negligible. \todo{Check for updated values for $y_s$ of $B_s$?} Further, we 
adopt the same values for common nuisance parameters of $i)$ the CKM quark-mixing
matrix, $ii)$ the charm and bottom quark masses in the $\overline{\rm MS}$ scheme,
and $iii)$ the parameterisation of subleading corrections in $1/m_b$ as
given in \cite{Beaujean:2013soa}.

@@

The most important change in the treatment of $B\to K$ form factors is the consistent
use of correlations available from lattice \cite{Bouchard:2013eph} for all three form
factors  $f_{+,T,0}$ in the construction of their prior. We use the $z$-parameterization
\cite{Khodjamirian:2010vf}, such that only five nuisance parameters --- see
\reftab{tab:hadronic:nuisance} --- arise due to the kinematical relation 
$f_0(0) = f_+(0)$.

@@

For $B\to K$ we have modified the prior of the nuisance parameter $f_+(0)$ of
the $f_+$ form factor parametrization w.r.t our previous analysis but kept the
slope parameter $b_1^+$ as is. This change accounts for both LCSR results
\cite{Khodjamirian:2010vf,Ball:2004ye} that use the same approach of
$B$-interpolating currents and on-shell $K$-mesons. As a result the prior on
$f_+(0)$ is wider and the tension between the SM prediction of the $B\to K
\ell\bar\ell$ branching ratio at $q^2 \in[1, 6]$~GeV$^2$~\cite{Khodjamirian:2012rm}
and the LHCb measurement \cite{Aaij:2012vr} is
reduced. Moreover, the recent lattice predictions \cite{Bouchard:2013eph} of the
form factor $f_+$ at high $q^2$ are included in our analysis as part of the
likelihood for technical reasons. For this purpose we reproduced lattice
predictions at three values
of $q^2 = 17,\, 20,\, 23$~GeV$^2$ as well as their correlation matrix based on
the parametrization given in \cite{Bouchard:2013eph}, see
\reftab{tab:btok-lattice}.  (The $q^2$ values and number of points are chosen
such that the correlation of neighboring points does not exceed $80\%$). This
constraint is included in the likelihood by means of a multivariate Gaussian.

>>>>

%%
%% Comments
%%
\newcommand{\danny}[1]{{\color{purple}{#1}}}
\newcommand{\eos}[1]{{\color{red}{#1}}}   % things to be checked and replaced with EOS results
\newcommand{\fred}[1]{{\color{green}{#1}}}
\newcommand{\todo}[1]{{\color{blue}{ {\bf ToDo: }{#1}}}}
\newcommand{\checked}[1]{{\color{magenta}{ {\bf Checked: }{#1}}}}

@@

\begin{figure*}
  \includegraphics[width=.24\textwidth]{plots/pdf/FH-1-6_vs_CT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/FH-15-22_vs_CT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-1-6_vs_CT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-15-22_vs_cT.pdf}
\\
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-1-6_vs_CT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-14-16_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-16-19_vs_CT.pdf}
  \caption{
    \eos{The sensitivity of $F_H^\mu$ [upper row: 1, 2], ${\cal B}(B^+ \to K^+ 
    \bar\mu\mu)$ [upper row: 3, 4] and ${\cal B}(B^0 \to K^{*0} \bar\mu\mu)$
    [lower row] integrated over $q^2$ at low and high $q^2$ to the tensorial
    coupling $\wilson{T}$. The bands represent the theory uncertainties at
    68\% probability. 
    For comparison two values of $\wilson[NP]{9} = 0$ (red) and $\wilson[NP]{9} 
    = -1.3$ (green) are shown together with the 68\% measurements of LHCb (blue).}
  }
  \label{fig:FHvsCT}
\end{figure*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\ 
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  \hline \hline
  $\mbox{Re}\,\wilson{T}$
  & \eos{$\quad$ $[-0.35,\, 0.20]$ ($[-0.55,\, 0.40]$) $\quad$}
  & \eos{$\quad$ $[-0.20,\, 0.15]$ ($[-0.35,\, 0.30]$) $\quad$}
  & \eos{$\quad$ $[-0.20,\, 0.20]$ ($[-0.40,\, 0.35]$) $\quad$}
  \\
  $\mbox{Im}\,\wilson{T}$
  & \eos{$[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)}
  & \eos{$[-0.15,\, 0.15]$ ($[-0.30,\, 0.30]$)}
  & \eos{$[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)}
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & \eos{$[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)}
  & \eos{$[-0.10,\, 0.20]$ ($[-0.25,\, 0.35]$)}
  & \eos{$[-0.20,\, 0.15]$ ($[-0.35,\, 0.35]$)}
  \\
  $\mbox{Im}\,\wilson{T5}$
  & \eos{$[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)}
  & \eos{$[-0.15,\, 0.15]$ ($[-0.30,\, 0.30]$)}
  & \eos{$[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)}
  \\
  \hline 
  $|\wilson{T}|$, $|\wilson{T5}|$
  & \eos{$< 0.35$ ($< 0.55$)}
  & \eos{$< 0.25$ ($< 0.35$)}
  & \eos{$< 0.30$ ($< 0.45$)}
  \\
  \hline 
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ --- [upper] 1D-marginalized 
     at 68\% (95\%) probability and [lower] 2D-marginalized --- when using
     measurements of $i)$ only $F_H^\mu$, $ii)$ $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $B_s \to \bar\mu\mu$), and $iii)$ allowing
     also new physics contributions to $\wilson{9,\,10}$ with uniform prior
     \eos{$\mbox{Re},\mbox{Im}(\wilson[NP]{i}) \in [-3,\, 3]$}.
  }
\end{table*}

In a scenario with only tensorial complex-valued couplings $\wilson{T,\, T5}$,
the experimental measurement of $F_H^\mu$ constrains the combination
$|\wilson{T}|^2 + |\wilson{T5}|^2$, up to some small interference of
$\wilson{T}$ with vectorial couplings $\wilson{7,\,7',\,9,\,9'}$. 
The according 68\% (95\%) 1D-marginalized probability intervals are listed in
\reftab{tab:cTT5:1-dimCLs}. As can be seen further in \reftab{tab:cTT5:1-dimCLs},
the constraints become tighter when utilising all observables in
\reftab{tab:observables}, mainly due to the branching ratio of $B\to K^{*} 
\bar\mu\mu$. The latter stronger bounds are driven by the new lattice
results of $B\to K^*$ form factors that yield too high predictions compared
to the measurements~\cite{Horgan:2013pva}. Since tensorial couplings contribute
constructively to ${\cal B}(B\to K^{*}\bar\mu\mu)$ large values are stronger
constrained. In this scenario, the measurements of $A_{\rm FB}^\mu$ does not pose
constraints due to vanishing scalar couplings and we find that the rate 
CP-asymmetries $A_{\rm CP}$ of $B\to K^{(*)} \bar\mu\mu$ do not provide 
constraints, therefore omitting them.

Eventually, we perform a fit with non-zero complex-valued $\wilson{9,\,10}$
by allowing uniform priors for \eos{$\mbox{Re, Im}(\wilson[NP]{i}) \in[-3,\, 3]$},
($i = 9,10$) in order to access the stability of the bounds derived from $F_H^\mu$
against destructive interference. In this case, $F_H^\mu$ by itself still provides 
bounds \eos{$|\wilson{T,\,T5}| < 0.5\,(0.8)$} at 68\% (95\%) probability that are
weakened by a factor of two since $F_H^\mu$ does not pose constraints on
$\wilson{9,\,10}$ (in the chosen prior range). Once additional experimental
measurements of \reftab{tab:observables}
are taken into account, the potential destructive effects of new physics
in $\wilson{9,\,10}$ become reduced and one recovers almost the same
constraints on $\wilson{T,\,T5}$ shown in \reftab{tab:cTT5:1-dimCLs}.
In consequence, the $F_H^\mu$ measurement~\cite{Aaij:2014tfa} of LHCb with
3 fb$^{-1}$ improves the previous bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$ 
by a \eos{factor of two}.

@@

The according four-parameter fit for real-valued scalar couplings to the data of
$\overline{\cal B}(B_s \to \bar\mu\mu)$ and $F_H^\mu$ results in the (2D-marginalized)
regions in the $(\wilson{i} \pm \wilson{i'})$ ($i = S, P$)  planes shown in
\reffig{fig:scalar}. The combination of $\overline{\cal B}(B_s \to \bar\mu\mu)$ 
and $F_H^\mu$ does not change when including the data of ${\cal B}$'s of $B\to 
K^{(*)}\bar\mu\mu$ --- remember that $A_{\rm FB}^\mu$ requires interference of
scalar with tensorial couplings. Quantitatively, the constraint from $\overline{\cal B}
(B_s \to \bar\mu\mu)$ on $(\wilson{i} - \wilson{i'})$ is about \eos{a factor five}
stronger than the one of $F_H^\mu$ on $(\wilson{i} + \wilson{i'})$.

\begin{figure*}
  \includegraphics[width=.325\textwidth]{plots/pdf/res-SSp.pdf}
%  \includegraphics[width=.32\textwidth]{plots/pdf/res-PPp.pdf}
  \includegraphics[width=.325\textwidth]{plots/pdf/res-SPplus.pdf}
  \includegraphics[width=.325\textwidth]{plots/pdf/res-SPminus.pdf}
  \caption{
    \eos{
    Constraints on real-valued scalar couplings $\wilson{S,\,S',\,P,\,P'}$ 
    from only $F_H^\mu$~(blue), only $\overline{\cal B}(B_s \to \bar\mu\mu)$ (green) 
    and their combination with other data in \reftab{tab:observables} as well as
    $\wilson{10} \in [-1,\, 9]$, $\wilson{10'} \in [-5,\,5]$ (red) 
    at 68\% (darker) and 95\% (lighter) probability. The constraints on 
    $(\wilson{P}Ê\pm \wilson{P'})$ are identical to $(\wilson{S}Ê\pm \wilson{S'})$
    [left], apart from a small shift of the contours by $(+0.2,\, 0.15)$.
    }
  }
  \label{fig:scalar}
\end{figure*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & only $\overline{\cal B}(B_s \to \bar\mu\mu)$
  & all
  \\ 
  set of couplings
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P'\,10,\,10'}$
  \\
  \hline \hline
  $\mbox{Re}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
  \\
  $\mbox{Im}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
  \\[0.1cm]
  $\mbox{Re}(\wilson{S} + \wilson{S'})$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  & $-$
  & \eos{$[-0.3,\, 0.4]$ ($[-0.6,\, 0.7]$)}
  \\
  $\mbox{Im}(\wilson{S} + \wilson{S'})$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  & $-$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} - \wilson{P'})$
  & $-$
  & \eos{$[0.06,\, 0.20]$  ($[0.02,\, 0.25]$)}
  & \eos{$[-0.10,\, 0.10]$ ($[-0.18,\, 0.18]$)}
  \\
  $\mbox{Im}(\wilson{P} - \wilson{P'})$
  & $-$
  & \eos{$[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$)}
  & \eos{$[-0.10,\, 0.10]$ ($[-0.20,\, 0.20]$)}
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} + \wilson{P'})$
  & \eos{$[-0.2,\, 0.6]$ ($[-0.5,\, 0.9]$)}
  & $-$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  \\
  $\mbox{Im}(\wilson{P} + \wilson{P'})$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  & $-$
  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
  \\
  \hline 
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cSP:1-dimCLs}
     The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$ --- 1D-marginalized 
     at 65\% (95\%) probability --- when using measurements of $i)$ only $F_H^\mu$,
     $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $iii)$ all the data in
     \reftab{tab:observables} allowing also for new physics contributions to 
     $\wilson{10,\,10'}$ with \eos{uniform prior $\mbox{Re}\,\wilson[NP]{10} \in [-1,\, 9]$,
     $\mbox{Im}\,(\wilson[NP]{10})$ and $\mbox{Re},\mbox{Im}\,(\wilson[NP]{10'}) \in [-5,\, 5]$}.
  }
\end{table*}

@@

We find that the experimental measurement of $F_H^\mu$
\begin{enumerate}
\item imposes by itself constraints on tensorial couplings \eos{$|{\cal C}_{T,\,T5}^\mu|
  < 0.35\, (0.55)$} at 68\% (95\%) probability, superseding previous bounds.
  In combination with current data from $B\to K^* \bar\mu\mu$ and lattice
  $B\to K^*$ form factors they become tighter \eos{$|{\cal C}_{T,\,T5}^\mu| < 0.30\, 
  (0.45)$}, even in the presence of non-standard contributions in vectorial
  couplings.
\item allows for the first time to bound all four scalar and pseudo-scalar 
  couplings due to it's complementarity to $\overline{\cal B}(B_s \to \bar\mu\mu)$.
  Even when taking into account destructive interference with vectorial couplings
  \eos{$|\wilson{i} + \wilson{i'}| < 0.4\, (0.7)$ and $|\wilson{i} - \wilson{i'}| < 
  0.1\, (0.2)$} for $i = S,P$. Currently, the bounds from $F_H^\mu$ are not as
  strong as those from $\overline{\cal B}(B_s \to \bar\mu\mu)$ by a factor four.
  Future measurements at LHCb and Belle II might change this, especially for 
  $\ell = e$. 
\item SM-EFT $\ldots$
\end{enumerate}
In all cases these \eos{constraints are weakened only slightly} in the presence of
new physics in vectorial couplings from destructive interference.

@@

Concerning numerical input, we refer the reader to~\cite{Beaujean:2013soa} for
the compilation of nuisance parameters and according values, whose uncertainties
are negligible. Further, we 
adopt the same values for common nuisance parameters of $i)$ the CKM quark-mixing
matrix, $ii)$ the charm and bottom quark masses in the $\overline{\rm MS}$ scheme,
and $iii)$ the parameterisation of subleading corrections in $1/m_b$ as
given in \cite{Beaujean:2013soa}.

@@

@@

As we do not make use of form factor relations for tensorial and scalar amplitudes
in $B\to K\bar\ell\ell$, additional nuisance parameters are included for the complete
set of $B\to K$ form factors $f_{+,T,0}$. As a consequence of using the 
$z$-parameterization \cite{Khodjamirian:2010vf}, only five nuisance parameters 
(listed in \reftab{tab:hadronic:nuisance}) arise due to the kinematical relation 
$f_0(0) = f_+(0)$. As prior information, the LCSR results~\cite{Khodjamirian:2010vf}
are adopted and supplemented with lattice determinations \cite{Bouchard:2013eph}.
The lattice results are given within a slightly different parameterisation necessitating
a conversion to the parameterisation used here. For this purpose, we generate the
form factors from the parameterisation \cite{Bouchard:2013eph}, including full
correlations, at three values of $q^2 = 17,\, 20,\, 23$ GeV$^2$ finding the results
compiled in \reftab{tab:btok-lattice}. (The $q^2$ values and number of points are chosen
such that the correlation of neighboring points does not exceed $80\%$.)
Subsequently, these ``data'' of the form factors is included in the likelihood
by means of a multivariate Gaussian in addition to experimental measurements.

@@
